% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{stereo vision}{camera  calibration}{local  matching}{seeds  propagation}{
planar constraint}

Binocular stereovision is an important research branch of computer vision, which 
can  restore  the  three-dimensional  depth  information  of  the  scene  by  computing  the 
disparity  of  space  points  in  two  images  of  the  same  scene.  Compared  with  the 
traditional  depth  measurement,  it  has  two  outstanding  advantages,  non-contact  and 
passiveness and it has been widely used in industrial inspection, aerospace,  robotics 
navigation, battlefield surveillance and other fields with these excellent features. 

In recent years, binocular stereovision method has got greater progress. However, 
there are still many problems to be solved, such  as camera  calibration accuracy  and 
stereo  matching  accuracy  problems,  which  need  the  researchers  to  propose  new 
solutions  continuously.  The  paper  carried  out  theory  and  technical  implementation 
research  on  the  camera  calibration,  stereo  matching  method,  and  stereovision 
measurement  error  and  accuracy  analysis  for  the  binocular  stereovision.  The  main 
work and innovations are as follows: 

1. In order to improve the accuracy of camera calibration,  the corner extraction 
algorithm  based  on  linear  fitting  of  the  initial  corner’s  limited  neighborhood  is 
proposed.  Harris  operator  is  employed  to  extract  the  checkerboard  corners 
preliminarily, the extracted checkerboard edge is implemented the linear fitting within 
the  certain  scope  of  the  initial  harris  corners  and  the  intersection  of  the  two  fitting 
lines is the final corner. The extracted corners are used to calibrate the stereo vision 
system  with  plane  calibration  method,  which  get  higher  calibration  accuracy,  the 
corner extraction method is proved to be effective.  

2.  In  order  to  get  a  better  balance  both  in  time  and  accuracy  of  local  stereo 
matching  algorithm.  A  fast  stereo  matching  algorithm  based  on  seeds  point 
propagation  is  presented.  The  joint  matching  cost  is  employed  to  measure  the 
difference  between  left  and  right  image  in  the  algorithm,  use  the  image  edge 
information  to  help  build  the  dynamic  matching  window,  which  can  weaken  the 
adverse  effects  of  the  fixed  window  and  obtain  high  quality  initial  disparity  map. 
After  the  seeds  point  selection  through  the  left  and  right  consistency  check  and 
regional characteristics, the seeds points are propagated with a variety of constraints. 
At last, the disparity map is refined with the regional vote. The algorithm can  get  a 
higher accuracy on most region of test images and has certain practical value.

3.  The  semi-global  stereo  matching  algorithm  based  on  the  disparity  planar 
constraints  is  put  forward  according  to  incomplete  of  the  optimal  path  in  the 
semi-global  algorithm.  We  establish  sparse  correspondences  by  extracting  FAST 
feature  points  and  ORB  descriptor  in  both  images.  The  sparse  disparity  points  are 
clustered  with  the  image  segmentation  and  propagate  to  other  points  in  the  same 
segmented  region.  The  reliable  disparity  points  of  the  segmented  region  are  carried 
out  the  planar  fitting  and  the  difference  between  the  plane  fitting  disparity  and  the 
initial disparity is added to the pixel matching cost as a constraint. Then, the optimal 
solution to the energy equation is obtained with the semi-global method. Experiments 
show  that  the  algorithm  can  work  well  in  the  region  with  textureless  and  repetitive 
structure  and  it  can  also  get  stable  matching  results  in  the  occlusion  and  depth 
discontinuity region while maintaining efficiency. 

4.  Some  factors  affecting  the  measurement  accuracy  in  the  binocular 
stereovision system are analyzed theoretically in detail. The theoretical derivation for 
the  three  aspects  of  the  camera  pixel  quantization  error,  structural  parameters  error, 
and  range  resolution  accuracy  are  launched  and  the  corresponding  conclusions  are 
drawn.  The  two  algorithms  are  tested  in  different  scenes.  At  last,  some  referenced 
suggestions for building the binocular stereovision ranging platforms are put forward 
with  the  method  of  combining  theoretical  derivation  with  the  experimental  data 
analysis. 
\end{Eabstract}
